\begin{thebibliography}{8}

\bibitem{tajs} Simon Holm Jensen, Anders M\o ller and Peter Thiemann. Type Analysis for JavaScript. \url{http://www.brics.dk/TAJS/}.
\bibitem{sa} Anders M\o ller and Michael I. Schwartzbach. Static Program Analysis. Department of Computer Science, Aarhus University, Denmark. January 30, 2013.
\bibitem{lamdapy} Shriram Krishnamurthi and Joe Gibbs Politz et. al. Python: The Full Monty, submitted OOPSLA 2013 paper, March 28, 2013
\bibitem{jython} The Jyhton Project: Python for the Java Platform \url{http://www.jython.org/}, June 26, 2013
\bibitem{pyref.datamodel} The Python Language Reference, Datamodel \url{http://docs.python.org/2/reference/datamodel.html}, May 13, 2013
\bibitem{pyref.constants} The Python Language Reference, Constants \url{http://docs.python.org/2/library/constants.html}, May 13, 2013
\bibitem{pyref.stdtypes} The Python Language Reference, Built-in Types \url{http://docs.python.org/2/library/stdtypes.html}, May 13, 2013
\bibitem{pyref.main} The Python Language Reference, \_\_main\_\_ \url{http://docs.python.org/2/library/__main__.html}, May 13, 2013
\bibitem{pyref.compound} The Python Language Reference, Compound Statements \url{http://docs.python.org/2/reference/compound_stmts.html}, May 20, 2013
\bibitem{pyref.typehierarchy} The Python Language Reference, The standard type hierarchy \url{http://docs.python.org/2/reference/datamodel.html#the-standard-type-hierarchy}, June 9, 2013
\bibitem{pyref.c3mro} The C3 method resolution order \url{http://www.python.org/download/releases/2.3/mro/}, June 9, 2013
\bibitem{recency} Gogul Balakrishnan and Thomas Reps. Recency-Abstraction for Heap-Allocated Storage \url{http://link.springer.com/chapter/10.1007/11823230_15}, June 10, 2013
\bibitem{lambdapy} Python: The Full Monty \url{http://cs.brown.edu/research/plt/dl/lambda-py/ae/index.html}, June 10, 2013
\bibitem{tool.pep8} pep8 - Python style guide checker \url{https://pypi.python.org/pypi/pep8}, June 26, 2013
\bibitem{tool.pyflakes} pyflakes - passive checker of Python programs \url{https://pypi.python.org/pypi/pyflakes}, June 26, 2013
\bibitem{tool.pychecker} PyChecker - Python source code checking tool \url{https://pypi.python.org/pypi/PyChecker}, June 26, 2013
\bibitem{tool.pylint} Pylint - python code static checker \url{https://pypi.python.org/pypi/pylint}, June 26, 2013
\bibitem{ide.appcelerator} Appcelerator: PyDev \url{http://pydev.org/}, June 26, 2013
\bibitem{ide.jetbrains} JetBrains. PyCharm \url{http://www.jetbrains.com/pycharm/}, June 26, 2013
\bibitem{ide.wingware} Wingware \url{http://wingware.com/}, June 26, 2013
\bibitem{django} Django \url{https://www.djangoproject.com/}, June 26, 2013
\bibitem{aopas} D.R. Chase, M. Wegman, and F. Zadeck. Analysis of pointers and structures. In \textit{Prog. Lang. Design and Impl.} pages 296-310, 1990.
\bibitem{starkiller} Michael Salib. Faster than C: Static type inference with Starkiller. \url{http://citeseer.ist.psu.edu/viewdoc/summary?doi=10.1.1.95.3786}, June 27, 2013
\end{thebibliography}
